### 2008-12-15 doc/infosys/TechnicalHandbook/ISIS - TechnicalHandbook.tex
Registrant configuration schema

%\documentclass{book}
\documentclass{article}                            %for shorter notes
\usepackage{graphicx}                              %for PNG images (pdflatex)
%\usepackage{graphics}                              %for EPS images (latex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref} %for \url tag
\usepackage{color}                                 %for defining custom colors
\usepackage{framed}                                %for shaded and framed paragraphs
\usepackage{textcomp}                              %for various symbols, e.g. Registered Mark
\usepackage{geometry}                              %for defining page size
\usepackage{longtable}                             %for breaking tables
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {Author Name},
  pdftitle = {Paper title},
  pdfsubject = {Paper subject},
  pdfkeywords = {Paper,keyword,comma-separated},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}                       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\globus}{Globus Toolkit\textsuperscript{\textregistered}~2~}
\newcommand{\GT}{Globus Toolkit\textsuperscript{\textregistered}}
\newcommand{\ngdl}{\url{http://download.nordugrid.org/}~}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%
%----- DON'T CHANGE HEADER MATTER
\begin{document}
\def\today{\number\day/\number\month/\number\year}

@@

  \verb# Read the configuration and store the information about the services in a list#\\
  \verb# do { // In a different Thread#\\

@@

>>>>

%\documentclass{book}
\documentclass{article}                            %for shorter notes
\usepackage{graphicx}                              %for PNG images (pdflatex)
%\usepackage{graphics}                              %for EPS images (latex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref} %for \url tag
\usepackage{color}                                 %for defining custom colors
\usepackage{framed}                                %for shaded and framed paragraphs
\usepackage{textcomp}                              %for various symbols, e.g. Registered Mark
\usepackage{geometry}                              %for defining page size
\usepackage{longtable}                             %for breaking tables
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {Ivan Marton},
  pdftitle = {ISIS Technical handbook},
  pdfsubject = {ISIS Technical handbook},
  pdfkeywords = {Paper,keyword,comma-separated},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}                       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\globus}{Globus Toolkit\textsuperscript{\textregistered}~2~}
\newcommand{\GT}{Globus Toolkit\textsuperscript{\textregistered}}
\newcommand{\ngdl}{\url{http://download.nordugrid.org/}~}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%
%----- DON'T CHANGE HEADER MATTER
\begin{document}
\def\today{\number\day/\number\month/\number\year}

@@

  \verb#Read the configuration and store the information about the services in a list#\\
  \verb#do { // Cyclic phase in a different Thread#\\

@@

\subsection{Configuration}
\label{Configuration}
The configuration of the different modules can be done through the ARC Configuration file. The format of these entries is shown by the relevant XSD Schema files.

\begin{framed}
Registrant.xsd\\
\\
\verb#<?xml version="1.0" encoding="UTF-8"?>#\\
\verb#<xsd:schema#\\
\verb#  xmlns:xsd="http://www.w3.org/2001/XMLSchema"#\\
\verb#  xmlns:registrant="http://www.nordugrid.org/schemas/RegistrantConfig/2008"#\\
\verb#  xmlns:arcConfig="http://www.nordugrid.org/schemas/ArcConfig/2007"#\\
\verb#  targetNamespace="http://www.nordugrid.org/schemas/RegistrantConfig/2008"#\\
\verb#  elementFormDefault="qualified">#\\
\verb# #\\
\verb#    <xsd:complexType name="Registrant_Type">#\\
\verb#        <!-- This element defines configuration of Information #\\
\verb#            Registration interface. -->#\\
\verb#        <xsd:sequence>#\\
\verb#            <!-- Period specifies how often registration to be done in seconds.#\\
\verb#                The missing or 0 value means a non period registration. -->#\\
\verb#            <xsd:element name="Period" type="xsd:nonNegativeInteger"/>#\\
\verb#            <!-- URL specifies contact endpoint of a bootstrap Information#\\
\verb#                Registration service. Further ISIS's adresses will be queried#\\
\verb#                from this service. -->#\\
\verb#            <xsd:element name="ISIS_URL" type="xsd:string" />#\\
\verb#            <!-- Optional KeyPath, CertificatePath, ProxyPath and CACertificatesDir#\\
\verb#                are paths to files storing X509 credentials used for establishing#\\
\verb#                connections. -->#\\
\verb#            <xsd:element name="KeyPath" type="xsd:string" minOccurs="0" />#\\
\verb#            <xsd:element name="CertificatePath" type="xsd:string" minOccurs="0" />#\\
\verb#            <xsd:element name="ProxyPath" type="xsd:string" minOccurs="0" />#\\
\verb#            <xsd:element name="CACertificatesDir" type="xsd:string" minOccurs="0" />#\\
\verb#        </xsd:sequence>#\\
\verb#    </xsd:complexType>#\\
\verb#    <xsd:element name="Registrant" type="registrant:Registrant_Type"/>#\\
\verb# #\\
\verb#    <!-- Optional element for Service element overriding the default Period length. -->#\\
\verb#    <xsd:element name="Period" type="xsd:nonNegativeInteger"/>#\\
\verb# #\\
\verb#</xsd:schema>#\\
\end{framed}
